\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-29 to-do2.tex
intuition for why result 2 holds in sequential model

						I just need to check that the extra $\bta$ will not mess up any results.

>>>>

						I believe that only Result 2 is in peril. A new term is added in the numerator (the denominator just gets a $(1-b^*)$; by the product rule, there are two terms after differentiating. The first is negative, the second is positive but can be combined with the pre-existing second term which just becomes less negative now. Should write all this up.
